Finding GENERAL Defect Prediction Models Within Hundreds of Software Projects

### 2020-04-17 response.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                               RESPONSE TO REVIEWERS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pagebreak
\newpage
\renewcommand*{\thesection}{\Alph{section}}
\nobalance
\section*{RESPONSE TO REVIEWERS}
\section*{Comments from the editor}

\review{I would like to thank the authors for submitting their work to TSE. While all the reviewers agree that the problem addressed is important and the paper has potential, the reviewers also identified several concerns that need to be carefully addressed. The reviewers also agreed that the amount of work needed to address those concerns is beyond a major revision. Thus, after carefully checking the reviewers and in accordance with reviewer’s recommendations, I also recommend “Revise and resubmit as New”.}

\response{ Thank you very much for your encouraging comments. We find that the prior draft made
several mistakes, that have been fixed here.
For example,  we assumed that the  core motivation for this work
was widely known and accepted in the community. That was a mistake so this draft completely rewrites the Introduction
to include much more background information on the 
presence of the problem studied here.}

\response{Next, using reviewer feedback, we can now better frame
our  research questions (this has the added benefit
of clarifying our discussion).}

\response{Apart from these two points, we have also addressed
the many helpful and detailed comments from the reviewers:
\be
\item The problem statement has been  clarified and properly positioned (R1, R3).
\item The novelty of the approach has  been clarified (R3). (see our comments to Reviewer3, in \bareresp{3-1},
below)
\item The study now includes all the details to ensure 
replicability   (R1, R2).
\item The results of the study were   be revisited and clarified. 
\item The background on transfer learning has been augmented, with more  citations (R2).
\item Using comments from  (R1, R2, R3), we have made numerous small editorial improvements.
\ee
}

@@

\section*{Reviewer 1}

\response{Thank you very much for your detailed review.
As we said to the associated editor, the previous draft made the following mistake:
\bi
\item We assumed that the  core motivation for this work
was widely known and accepted in the community. That was a mistake. 
\item
Consequently, this draft completely rewrites the Introduction
to include much more background information on the 
presence of the problem studied here.
\ei
We have made some additional corrections, clarifications, and revisions, as directed by your comments. To assist in your review, we refer to specific locations of each of the changes using \respto{1-XX}.}

@@

\review{(1.1a) Background. The paper builds upon a number of previous studies. However, several key questions have no answer: *What is* the bellwether? *Why is* this relevant? How does it work when applied to different contexts? Why is this useful in practice?}

\response{You are quite correct, we did not define bellwether till very late in the prior draft. In this draft, we define bellwether on page 1\citeresp{1-1a}} where we say:

\begin{quote}
    \response{Given a community of projects developed by the same organization,
the ``bellwether'' is a project or a handful of projects
whose data yields the best analytic (i.e. defect prediction, effort estimation, etc) on all others}\footnote{We call that the ``bellwether'' since that is the
name of the  leading sheep of a flock, with a bell on its neck.}
\end{quote}

@@

\response{Thank you for that comment.  You are quite correct-- we did not document the source of our intuition. We have added the following note to \citeresp{1-1b}}

\begin{quote}
\response{``The core intuition of this new approach is two-fold. Firstly,
many projects are similar in structure. We came to this
intuition based on the writing
of    Devanbu
et al.`\cite{hindle2012naturalness}   who showed that a remarkably
small number of Markov chains 
capture the repeated patterns
of tokens in a program~\\
When such similarities
exist, then we   exploit symmetries between different projects in order to learn predictors from one and apply those to another. Specifically: assuming inter-project symmetry,   we do not need to run comparisons between all pairs of projects since analyzing just a few pairs should work as well as anything else.''}
\end{quote}

\review{(1.2)The relevance of the paper. This is, unfortunately, unclear. According to the abstract and introduction, the main issue treated in the paper is related to scalability. Please, provide a clear case study on the performance of bellwether methods. The claims on the scalability of the approaches are just claims, no details are reported. Abstract and introduction just report that "when applied to the 697 projects studied here, they took 60 days of CPU to find and certify the bellwether". As said, the bellwether approach has been applied to several problems (e.g., defect prediction/effort estimation/bad smell detection): are these problems the same? When is it needed to apply scalable solutions for bellwether approaches? Why? Please, explain.}

\response{Thank you for your comments.
 On review, we found that the core problem of conclusion instability
was not well documented in the introduction. This new draft fixes that problem with an extensively revised introduction~\citeresp{1-2} that better focuses the work on conclusion instability and scalability.}

@@

% {need a new RQ0: how slow is standard bellwether. theoretically an empirically its slow (chart on p2. move to RQ0). May need to include results using increasing community size.XXX including an comparison study with varying size of community to start with. Still need to write this}

\review{(1.3a) Writing style. The introduction is, simply, to be completely rewritten}

\response{Thank you for your comment. We agree.   Much of the new
text on page1 ~\citeresp{1-3a} takes care to document {\em why }
we are exploring conclusion instability before
moving on the {\em how} we do that exploration.}

@@

\review{(1.3a)I would like to see a paper that is understandable even from non-experts. As such, please define the context of the paper, the concepts of (1) software quality - line 1, (2) general models - line 2, (3) many projects - line 2, (4) "scalable approach to learning effective models adapted to the task at hand" - line 2/3, (5) "or does the truth lie somewhere in-between" - line 3. These are just of the examples of why the introduction is unclear and does not provide any detail on the reasons behind the paper. The same is true for the remaining of the paper, which gives for granted many of the concepts without explaining them properly.}

\response{Thank you for your comment. We have deleted much of that confusing terminology from the introduction since, as you say, it introduces too many ideas in a confusing way, all at once.  Please see \citeresp{1-3}.}

\review{(1.4) Please, avoid claims such as "have tremendous practical significance" without providing any practical significant example/citation. (This is just an example)}

\response{ Thank you for your comment, You are right. In this manuscript, we have deleted the  superlatives (including that one)}

@@

\review{(1.5a) The clarity and replicability of the paper are unclear. Here some examples 1) "The logistic regression learner (since it is relatively fast)". What does "fast" mean? How was "fast" computed? }

\response{ Thank you for your comment, you are quite right. We had not properly mentioned the reason behind choosing logistics regression.  In this draft, we have added the reasons to \citeresp{1-5a}:}

\begin{quote}
\response{
"The logistic regression learner,  since it is widely used in defect prediction~\cite{ghotra2015revisiting,zhang2017data,he2012investigation,nam2013transfer,pan2010domain} in   the  software engineering domain and, in our experience,
it runs much faster (in terms of model building time) than many other learners such as Support Vector Machine, Random Forest, Artificial Neural Nets etc, (when tested on defect prediction).}
\end{quote}

@@

\review{(1.5b) "The SMOTE class imbalance correction algorithm [49], which we run on the training data2". Why is SMOTE needed? Why is the problem unbalanced? Please, explain.
}

\response{You are right, we had not included the reason for using SMOTE in our algorithm and had not explained why the problem is unbalanced. In this draft, we have added notes to answer those questions \citeresp{1-5b}:}
\begin{quote}
    \response{(we used)... The SMOTE class imbalance correction algorithm~\cite{Chawla2002} since many of the projects have relatively very few or a large number of defects. A model built on a project with such skewed class distribution can result in a biased model towards the majority class (Such models can either have a low recall or a high recall with high pf). Thus we run SMOTE on the training data to artificially boost the number of target examples in the training data and achieving balanced recall and pf for the minority class test examples}
\end{quote}

@@

\review{(1.5c) "and Hall’s CFS feature selector". Which features have been removed and why?
}

\response{You are quite correct, we did not include the details about how the features are being removed and why in the last draft. In this draft, we have included notes regarding how CFS works and why the features that are not used are removed \citeresp{1-5b}:}

\begin{quote}
    \response{Hall's CFS feature selector~\cite{hall1999correlation} is used to identify features which are highly correlated with the classification, yet uncorrelated to each other. The features which are  highly correlated with each other will not add more information while making classification, while the features which are uncorrelated towards the classification also not add more information while making classification. The CFS algorithm incrementally picks one feature at a time which add the most information towards the classification at a given step and stops when there is no more improvement in the score.}
\end{quote}

\response{As to what attributes were selected, please see Figure~\ref{fig:FSS_level1}. As to what of
the selected figures were most important, please see Table~\ref{tbl:coefs_4}.}

@@

\review{(1.5d) "As to CFS, we found that without it, our recalls were very low and we could not identify which metrics mattered the most". Where can the reader understand this statement? Where is the replication data?}

\response{Thank you for your comment, using the replication package (including data) the experiments can be reproduced \citeresp{1-5d}.  Also, we have added in specific numbers to that sentence:
\begin{quote}
As to CFS, we found that without it, our recalls were very low (less than 20\%).
\end{quote}
}

@@

\review{(1.5e) "extensive studies have found that CFS more useful than many other feature subset selection methods such as PCA or InfoGain or RELIEF". The paper cites just one paper, how should these studies be "extensive"?}

\response{Thank you for that comment.  You are quite correct-- we did not document all the necessary citations for supporting our claim before. We have added the following note to \citeresp{1-5e}}

\begin{quote}
    {\color{blue}Also,   extensive studies have found that CFS more useful than many other feature subset selection methods such as  PCA or InfoGain or RELIEF\respto{1-5e} ~\cite{hall1999correlation,challagulla2008empirical,arar2015software,lee2016developer,rodriguez2007attribute,gao2015combining,hosni2017investigating}. }
\end{quote}

@@

\review{(1.5f) "Maximize recall and precision and popt(20)": Why should these metrics be maximized? What is the practical value, e.g., is high recall always needed in practice, or should we prefer precision in the problems treated by the bellwether? What about popt(20)?}

\response{Thank you for your comment, we didn't explain why these metrics need to be maximized, For those notes, please see \citeresp{1-5f} and \citeresp{1-5g}.}

@@

\review{(1.5g) "While minimizing false alarms and ifa auc": Again, please explain the practical relevance of the performance metrics employed. }

\response{Thank you for your comment, we didn't explain why these metrics need to be maximized, For those notes, please see  \citeresp{1-5f} and \citeresp{1-5g}.}

\review{(1.5h) 
More in general, how can one replicate the performed study? Is there a replication package? If so, where?}

\response{Thank you for that comment. You are quite correct-- we did not include in-depth steps to replicate the study before. We have added a replication package in contribution section \citeresp{1-5h} as well as more in-depth details about the algorithm has been added in Figure~\ref{fig:Pseudo-code} and section~\ref{GENERAL}.}

@@

\review{(1.6a) The analysis of the results should be substantially improved. Let consider the case of Section 5 - RQ1. The results are reported in less than half column and refer to a figure (Figure 6) which does not explain anything. The summary reports that "Theoretically and empirically, the hierarchical reasoning on GENERAL performs much faster than standard bellwether methods": I cannot understand where these "theoretically and empirically" come from, since there is no proof of them. }

\response{You are quite correct. In the last draft we indeed did not include a detailed analysis of the results to show the scalability of our model. In this draft \citeresp{1-2}\citeresp{1-6a} we have included 2 more research questions (RQ1 and RQ2) to show the conventional bellwether is slower than the new bellwether (aka GENERAL) method. We also have updated another research question (RQ3) to compare the methods in-term of number of comparisons and time taken to run the two methods, as can been seen in Figures~\ref{fig:compare_time} and
\ref{fig:compare}.}

\review{(1.6b) What makes the reported method scalable?}

\response{Thank you for your comment, in this version we have updated the RQ3 to show that our method is scalable. We have showcased the analysis of number of comparisons and run time between the two algorithms (conventional bellwether and GENERAL) using various community sizes.}

@@

\section*{Reviewer 2}

\response{Thank you very much for your detailed review.
As we said to the associated editor, the prior draft  assumed that the core motivation for this work was widely known and accepted in the community. That was a mistake so this draft completely rewrites the Introduction to include much more background information on the presence of the problem studied here. Also, thanks to your feedback, 
we have made some additional corrections, clarifications, and revisions, as directed by your comments. Please note that to assist in your review, we refer to specific locations of each of the changes using the notation \respto{2-XX}.}

\response{Before going on, we need to ask you one thing.
\begin{itemize}
\item
Several   of your comments take issue with two terms used in this paper ``lessons learned'' and "transfer learning".
We agree with you that our use of ``lessons learned" was inappropriate and we have removed all terms from this paper.
\item
But as to your argument that our use of ``transfer learning'' is  incorrect, that is not clear to us. 
As near as we can tell, our use of transfer learning is compatible with standard definitions in that field, both outside
of SE (e.g. Pan's paper~\cite{pan2009survey})
and within the SE literature~\cite{ma2012transfer,zimmermann2009cross,turhan2009relative,krishna2018bellwethers,jing2015heterogeneous,he2014towards,nam2017heterogeneous,cheng2016heterogeneous,yu2017feature}.
Also, reading through your comments, one thing that strikes us is that perhaps you are reserving the use of ``transfer learning''   only  to heterogeneous learning (where the source and target have different attributes)?  If so, then perhaps 
  \S\ref{tion:how1} is relevant since, in that section, we carefully define and distinguish between homogeneous and heterogeneous transfer learning and clearly state that this paper 
is about homogeneous learning, where the attributes are the same in source and target.   
\item
That said, we want to work with you on this point. Is there another term you would accept that is not ``lessons learned'' or ``transfer learning''?
Would the terms ``generalize'' or ``extend'' work for you? Please advise.
\end{itemize}}

@@

% \response{ ur rught we renamed as you said. }

\review{(2.2) [Sec. 1] “…the bellwether is equivalent to the other models…” This claim is confusing. 1) Is “the bellwether” a model or a project? 2) How is equivalence defined? Or do you simply mean “similar”?}

\response{ Thank you for your comment, in the last draft we did not accurately explain what bellwether is. In this draft we have included the definition of bellwether \citeresp{1-1a}\citeresp{2-2}:}

\begin{quote}
    \response{(a) `Given a community of projects developed by the same organization,
the ``bellwether'' is a project or  a handful of projects
whose data yields the best analytic (i.e. defect prediction, effort estimation, etc) on all others.} 
\end{quote}
\begin{quote}
    \response{Also, to answer your second question, ``…the bellwether is equivalent to the other models'' means ``bellwether is an exemplar project for the community of N projects seen so far''  }
\end{quote}

@@

\review{(2.3) [Sec. 1] “when new projects appear, their quality can be evaluated even before there is an extensive experience base within that particular project (again, just by studying the bellwether).” }

\response{Thank you for your comment, this was a needless complexity that we deleted from this draft.}

\review{(2.4) If the point is to use the bellwether to infer things about a “new” project, then how new can the new project be? When (in the new project’s history) can you be sure the model from the bellwether is valid to use?}

\response{Thank you for your comment. To answer the first question, the projects can be completely new projects, without any historical data collected for reference. To answer the second question, in this research the experiments have been designed to simulate a situation, where there are known projects in a large community as well as a set of new projects which are not part of the community. We do this by dividing the 697 projects into two sets 1) {\em Train 1}: a community 627 projects, from which we will select a bellwether and 2) {\em Train 2}: a set of 70 new projects, which will be tested using bellwether.}

@@

% \response{Explain the train, test splits and the how you do the exp. then say this is what our model proves, it predicts for projects which it has not seen before XX.}

\review{(2.5) Do you have to find a bellwether for each purpose? In other words, if you find a bellwether among 697 projects for defect rate prediction, then is that same bellwether automatically used to build a model for another discrete task (different than defect rate prediction)? Or will you have to apply this algorithm for each and every discrete task?}

\response{Thank you for your comment. 
As you point out, the prior draft
was too vague on this point.
This paper now focuses on defect prediction (see the new title).}

\response{ But to answer
your question (about whether
or not the bellwether changes
per goal), it is possible that another
task will require another bellwether.
Accordingly,
we assert it is vital that the
bellwether method is fast. Hence this paper.}

@@

\review{(2.6) Figure 1 needs to be omitted}

\response{You are correct. We have deleted Figure 1 from this manuscript. }

\review{(2.7) The computational complexity $(O(N^2)$ versus $O(m*(N/m^2))$ is both compact appropriate.}

\response{In practice, the difference
between the runtimes associated with these two  approaches is a 
very large difference (as witnessed
by  Figures~\ref{fig:compare_time} and ~\ref{fig:compare}.) }

@@

\review{(2.8) The paper does not evaluate the model’s performance using a pool of 12,000 projects; the evaluation does not even use 1,000 projects.}

\response{Yes, are correct. That was our mistake. All our current numbers now say 697.}

@@

\review{(2.9) [Sec. 1] The box under RQ4 is very confusing. We find the bellwether to simply study one project, but this note says we still need to analyze hundreds of projects to understand something like the importance of features. Is this right?}

\response{You are correct-- that text was confusing. In this reworked version, that text is removed. .}

@@

\review{(2.17) [Sec. 2.4] “Successful transfer learning can have two variants…” Cite these variants. This is a software engineering paper—not a machine learning paper—that should reference other work for these fundamental details.}

\response{Thank you for your comment. We indeed forgot to add the citations in the previous manuscript. We have added the citations in this manuscript \citeresp{2-17}.}

\review{(2.18) [Sec. 3.2] “…for large sample datasets…” What is the size of the design matrix? Does 21 product metrics and five process metrics mean 26 columns? If there are 697 projects and snapshots every six months, then how many rows are there?}

\response{Thank you for your comment, the previous manuscript did not included all the details regarding the design matrix. In this manuscript we have included much details regarding the design matrix in \citeresp{2-18}. \fig{meta} shows the distribution of number of rows in each projects, which is a snapshots of the projects from 6 months back of the last commit. We can see from the \fig{meta} median number of rows is around 120 in this group of 697 projects explored. We have also added following notes to~\citeresp{2-18} to explain the metrics collected:}

\begin{quote}
    \response{...using the   Understand tool~\cite{visualize},
we calculated different variations (i.e. average, max etc.) of 21 product and 5 process metrics, with a total 66 attributes/columns to build defect prediction models
 (see Table~\ref{tbl:metric}).
These product  metrics are calculated from snapshots of the projects from 6 months back of the last commit. The process metrics are computed using the change history in the six-months period before the split date via manual collection of data using scripts.}
\end{quote}

@@

\review{(2.25) [Sec. 3] What are the units for dataset size in Fig. 4?}

### 2020-04-17 manuscript.tex
Updates from Overleaf

%\usepackage{hyperref}
%\usepackage{cleveref}
\usepackage{colortbl}
\newmdenv[
  tikzsetting= {fill=light-gray},
  linewidth=1pt,
  roundcorner=0pt, 
  shadow=false
]{myshadowbox}
\usepackage{colortbl} 
\usepackage{subcaption}
\usepackage{blindtext, graphicx}
\usepackage{textcomp}
\usepackage{mathtools}
\usepackage[hidelinks]{hyperref}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{caption}
\usepackage{color}
\usepackage[final]{listings}
\usepackage{graphicx} 
\usepackage{multirow}
\usepackage{balance}
\usepackage{picture}
\usepackage{relsize}
\usepackage{multicol}
\usepackage{soul}
\usepackage{enumitem}
\setitemize{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*}
\setenumerate{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*}
\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
\usepackage{array}
\usepackage{makecell}
\usepackage{bigstrut}
\newcommand{\tion}[1]{\S\ref{sect:#1}}
\newcommand{\fig}[1]{Figure~\ref{fig:#1}}
\newcommand{\tab}[1]{Table~\ref{tab:#1}}

\newcommand{\tbl}[1]{Table~\ref{tbl:#1}}
\definecolor{comment_color}{rgb}{0.5, 0, 1}
\definecolor{steel}{rgb}{0.1, 0.3, 0.5} 
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\newcommand{\todoc}[2]{{\textcolor{#1}{\textbf{[[#2]]}}}}
\newcommand{\todobrown}[1]{\todoc{green}{\textbf{[[#1]]}}}
\newcommand{\todoblue}[1]{\todoc{blue}{\textbf{[[#1]]}}}
\newcommand{\todoorange}[1]{\todoc{cyan}{\textbf{[[#1]]}}}
\newcommand{\todored}[1]{\todoc{red}{\textbf{[[#1]]}}}
\newcommand{\rahul}[1]{{\textcolor{steel}{#1}}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\usepackage[
 pass,% keep layout unchanged
 % showframe,% show the layout
]{geometry}
\usepackage[skins]{tcolorbox}
\usepackage{verbatim}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage[export]{adjustbox}
\usepackage{mathtools}
\setlength{\belowcaptionskip}{-10pt}
\renewcommand{\footnotesize}{\scriptsize}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\definecolor{lightgray}{gray}{0.8}
\definecolor{LightCyan}{rgb}{0.88,1,1}
\definecolor{darkgray}{gray}{0.7}
\definecolor{Gray}{rgb}{0.88,1,1}
\definecolor{Gray}{gray}{0.85}
\definecolor{Blue}{RGB}{0,29,193}
\definecolor{MyDarkBlue}{rgb}{0,0.08,0.45} 
\definecolor{pink}{RGB}{231,95,110}
\definecolor{lightergray}{rgb}{0.85, 0.85, 0.85}
\definecolor{darkgray}{rgb}{0.47, 0.47, 0.47}
\definecolor{lightestgray}{rgb}{0.95, 0.95, 0.95}
\definecolor{ao(english)}{rgb}{0.0, 0.5, 0.0}
% \frenchspacing
\lstset{
  language=Python,
  basicstyle=\sffamily\fontsize{2.5mm}{0.8em}\selectfont,
  breaklines=true,
  prebreak=\raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
  frame=l,
  showtabs=true,
  columns=fullflexible,
  showspaces=false,
  showstringspaces=false,
  keywordstyle=\color{pink}\bfseries\sffamily\fontsize{2.8mm}{0.6em},
  emph={train, predict, add_samples, FindBellwether, BEETLE, get_cost, sample, get_perf, remove_non_bellwethers, LinearTransform, GPTransform,General,get_featrures,BIRCH,bellwether,get_bellwethers,O(N)}, 
  emphstyle=\bfseries\color{blue!50!black} ,
  stringstyle=\itshape\color{black!50},
  commentstyle=\color{red!50!black}\it,
  numbers=left,
  captionpos=t,
  escapeinside={\%*}{*)}
}

\newcommand{\response}[1]{\textcolor{blue}{#1}}
\usepackage[tikz]{bclogo}
\newenvironment{RQ}[1]%
{\noindent\begin{minipage}[c]{\linewidth}%
\begin{bclogo}[couleur=gray!20,%
                arrondi=0.1,logo=\bctrombone,% 
                ombre=true%
                ]{{\small  ~#1}}}%
{\end{bclogo}\vspace{2mm}\end{minipage}}

@@

\newcommand{\flash}{{\sc Flash}\xspace}
\usepackage{soul}
\usepackage{color}

@@

\usepackage{amsmath}
\definecolor{Gray}{gray}{0.95}
\definecolor{LightGray}{gray}{0.975}

@@

@@

\IEEEtitleabstractindextext{%
\begin{abstract}
% \respto{2-22}{\color{blue}Given a group of software projects,
% there often exists  one   exemplar project
% that offers the best prediction for all others.
% Such ``bellwether projects''
% can be used to make quality predictions that are general
% to that group.}
% Existing  methods  for  finding bellwether  are  very slow.  When  applied  to  the  697  projects  studied  here, standard bellwether methods   took  60  days  of  CPU  to  find  and  certify  the  bellwethers
% Hence,we  propose a faster way to find bellwethers. 
% GENERAL applies hierarchical clustering to groups of project data. At each level within a tree of clusters, one bellwether is computed from sibling projects, then promoted up the tree. This hierarchical method is a scalable approach to learning effective models from very
% large data sets. For  hundreds of projects, the defect prediction models generated from GENERAL's bellwether were just as good as those found via  standard methods.

\respto{2-22}{\color{blue}Given a group of software projects, there often exists  one   exemplar project that offers the best prediction for all others. Such ``bellwether projects'' can be used to make quality predictions that are general to that group.} Existing  methods  for  finding bellwether  are  very slow.  When  applied  to  the  697  projects  studied  here, standard bellwether methods   took  60  days  of  CPU  to  find  and  certify  the  bellwethers. Also among a large group of software projects there may be subgroup of projects which are more similar to each other then other subgroups and can have a bellwether for each such subgroup of projects. Existing bellwether methods does not take this into consideration to find multiple bellwether. Hence, we  propose a faster and better  way to find bellwethers. GENERAL applies hierarchical clustering to groups of project data. At each level within a tree of clusters, one bellwether is computed from sibling projects, then promoted up the tree. This hierarchical method is a scalable approach to learning effective models from very large data sets. For  hundreds of projects, the defect prediction models generated from GENERAL's bellwether were just as good as those found via standard methods.

@@

\begin{IEEEkeywords}
Transfer Learning, Bellwether, Defect Prediction, Software Analytics. 
\end{IEEEkeywords}}

@@

\respto{1-2}\respto{1-3}{\color{blue} Researchers and industry practitioners makes use of data-driven decision making data mining algorithms build software quality models from project data.For example, many research and industrial groups generate defect predictors from software metrics~\cite{ghotra2015revisiting, zimm09 ,okutan2014software, he13, Zhang16aa, nam2017heterogeneous, Me13, Tantithamthavorn18, me09b, me10a, peters2015lace2, nam2018heterogeneous, menzies2011local, zimmermann09}. These metrics can take  forms including process metrics (that describe how and who updates the code) and product metrics (such as number of methods per class, lines of codes, etc). One advantage of this approach is that the collection of these metrics is very fast.
Also,  the subsequent data mining (to generate the quality models) can be fully automated and can scale to a large number of projects. Hence, data-driven decision making  is widely used in   SE research and   industrial practice.~\cite{tosun2010ai,kim2015remi,wan2018perceptions} }

@@

{\color{blue} But what is the external validity of the conclusions reached  via
the these data mining methods? Prior to this paper, the usual result is that such conclusions are not general to multiple projects. For example, Table~\ref{unstable} summarizes the results of dozens of studies. In that table we observe that, from project to project, very different attributes are most associated with defect prediction. This is troubling since,   as
Sawyer et al. argue,   project-general
insights are the key driver for businesses to invest in data analytics.
If  new models keep being generated whenever we switch to  new projects, then that exhausts the ability of  users to draw insight from  new data.
Hassan~\cite{Hassan17} cautions that managers lose faith in software analytics if its models keep changing since  the assumptions used to make prior policy decisions may no longer hold. 
 Further,
if we are unsure what factors most influence quality, it is difficult to design and implement and deploy tools that can successfully improve that quality.
Lastly,
consider the task of training a   novice software engineers or newcomers to a project. If our models are not stable, then it hard to teach what factors  most influence software quality.}

>>>>

%\usepackage{hyperref}
%\usepackage{cleveref}
% \usepackage{colortbl}
\newmdenv[
  tikzsetting= {fill=light-gray},
  linewidth=1pt,
  roundcorner=0pt, 
  shadow=false
]{myshadowbox}
\usepackage{colortbl} 
% \usepackage{subcaption}
\usepackage{blindtext, graphicx}
\usepackage{textcomp}
% \usepackage{mathtools}
\usepackage[hidelinks]{hyperref}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{caption}
\usepackage{color}
\usepackage[final]{listings}
% \usepackage{graphicx} 
% \usepackage{multirow}
\usepackage{balance}
\usepackage{picture}
\usepackage{relsize}
\usepackage{multicol}
\usepackage{soul}
\usepackage{enumitem}
\setitemize{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*}
\setenumerate{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*}
\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
% \usepackage{array}
\usepackage{makecell}
\usepackage{bigstrut}
\newcommand{\tion}[1]{\S\ref{sect:#1}}
\newcommand{\fig}[1]{Figure~\ref{fig:#1}}
\newcommand{\tab}[1]{Table~\ref{tab:#1}}

\newcommand{\tbl}[1]{Table~\ref{tbl:#1}}
\definecolor{comment_color}{rgb}{0.5, 0, 1}
\definecolor{steel}{rgb}{0.1, 0.3, 0.5} 
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\newcommand{\todoc}[2]{{\textcolor{#1}{\textbf{[[#2]]}}}}
\newcommand{\todobrown}[1]{\todoc{green}{\textbf{[[#1]]}}}
\newcommand{\todoblue}[1]{\todoc{blue}{\textbf{[[#1]]}}}
\newcommand{\todoorange}[1]{\todoc{cyan}{\textbf{[[#1]]}}}
\newcommand{\todored}[1]{\todoc{red}{\textbf{[[#1]]}}}
\newcommand{\rahul}[1]{{\textcolor{steel}{#1}}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\usepackage[
 pass,% keep layout unchanged
 % showframe,% show the layout
]{geometry}
\usepackage[skins]{tcolorbox}
\usepackage{verbatim}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage[export]{adjustbox}
% \usepackage{mathtools}
\setlength{\belowcaptionskip}{-10pt}
\renewcommand{\footnotesize}{\scriptsize}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
% \definecolor{lightgray}{gray}{0.8}
\definecolor{LightCyan}{rgb}{0.88,1,1}
\definecolor{darkgray}{gray}{0.7}
\definecolor{Gray}{rgb}{0.88,1,1}
\definecolor{Gray}{gray}{0.85}
\definecolor{Blue}{RGB}{0,29,193}
\definecolor{MyDarkBlue}{rgb}{0,0.08,0.45} 
\definecolor{pink}{rgb}{231,95,110}
\definecolor{lightergray}{rgb}{0.85, 0.85, 0.85}
\definecolor{darkgray}{rgb}{0.47, 0.47, 0.47}
\definecolor{lightestgray}{rgb}{0.95, 0.95, 0.95}
\definecolor{ao(english)}{rgb}{0.0, 0.5, 0.0}
% \frenchspacing
\lstset{
  language=Python,
  basicstyle=\sffamily\fontsize{2.5mm}{0.8em}\selectfont,
  breaklines=true,
  prebreak=\raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
  frame=l,
  showtabs=true,
  columns=fullflexible,
  showspaces=false,
  showstringspaces=false,
  keywordstyle=\color{pink}\bfseries\sffamily\fontsize{2.8mm}{0.6em},
  emph={train, predict, add_samples, FindBellwether, BEETLE, get_cost, sample, get_perf, remove_non_bellwethers, LinearTransform, GPTransform,General,get_featrures,BIRCH,bellwether,get_bellwethers,O(N), if, else, in,for, return}, 
  emphstyle=\bfseries\color{blue!50!black} ,
  stringstyle=\itshape\color{black!50},
  commentstyle=\color{red!50!black}\it,
  numbers=left,
  captionpos=t,
  escapeinside={\%*}{*)}
}

\newcommand{\bluecheck}{}%
\DeclareRobustCommand{\bluecheck}{%
  \tikz\fill[scale=0.4, color=blue]
  (0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;%
}

\newcommand{\response}[1]{\textcolor{blue}{#1}}
\usepackage[tikz]{bclogo}
\newenvironment{RQ}[1]%
{\noindent\begin{minipage}[c]{\linewidth}%
\begin{bclogo}[couleur=gray!20,%
                arrondi=0,logo=\none,% 
                ombre=true%
                ]{{\small  ~#1}}}%
{\end{bclogo}\vspace{2mm}\end{minipage}}

@@

\newcommand{\flash}{{\sc Flash}\xspace}
% \usepackage{soul}
\usepackage{color}

@@

% \usepackage{amsmath}
\definecolor{Gray}{gray}{0.95}
% \definecolor{LightGray}{gray}{0.975}

@@

\usepackage{tcolorbox}
\newtcolorbox{blockquote}{colback=black!5,boxrule=0.4pt,colframe=black,fonttitle=\bfseries}

@@

\IEEEtitleabstractindextext{%
\begin{abstract}

\respto{2-22}{\color{blue}Given a large group of software projects, there often exists  a few   exemplar project(s) that offers the best prediction for all others. Such ``bellwether projects'' can be used to make quality predictions that are general to many other projects.}

Existing  methods  for  finding bellwether  have two problems. Firstly, they are  very slow.  When  applied  to  the  697  projects  studied  here, standard bellwether methods   took  60  days  of  CPU  to  find  and  certify  the  bellwethers.
Secondly, they assume that only one bellwether exists and, amongst hundreds of projects, they may exist  subgroups, each of which requires their own bellwether.

GENERAL is a new bellwether method that addresses both problems. GENERAL   applies hierarchical clustering to groups of project data. At each level within a tree of clusters, one bellwether is computed from sibling projects, then promoted up the tree.  In this way, GENERAL can find multiple
bellwethers, if they exist. Also, GENERAL's hierarchical decomposition runs much faster (and scales better) than standard
bellwether methods.

@@

\begin{IEEEkeywords}
Transfer Learning, Bellwether, Defect Prediction, Software Analytics, Logistic Regression. 
\end{IEEEkeywords}}

@@

\respto{1-2}\respto{1-3}{\color{blue} Researchers and industry practitioners make use of data-driven decision making data mining algorithms to build software quality models from project data. Many research and industrial groups generate defect predictors from software metrics~\cite{ghotra2015revisiting, zimm09 ,okutan2014software, he13, Zhang16aa, nam2017heterogeneous, Me13, Tantithamthavorn18, me09b, me10a, peters2015lace2, nam2018heterogeneous, menzies2011local, zimmermann09}. These metrics can take  forms including process metrics (that describe how and who updates the code) and product metrics (such as the number of methods per class, lines of codes, etc). When the creation of such models is fully automated
(using data mining), then this approach scales a large number of projects. Hence, data-driven decision making  is widely used in   SE research and   industrial~\cite{tosun2010ai,kim2015remi,wan2018perceptions}. }

@@

{\color{blue} But what is the external validity of the conclusions reached  via these data mining methods? Prior to this paper, the usual result is that such conclusions are not general to multiple projects. Table~\ref{unstable} summarizes the results of dozens of studies. In that table, from project to project, very different attributes are most associated with defect prediction. This is troubling since,   as
Sawyer et al. argue,   project-general
insights are the key driver for businesses to invest in data analytics. If  new models keep being generated whenever we switch to  new projects, then that exhausts the ability of  users to draw insight from  new data.
Hassan~\cite{Hassan17} cautions that managers lose faith in software analytics if its models keep changing since  the assumptions used to make prior policy decisions may no longer hold. 
 Further,
if we are unsure of what factors most influence quality, it is difficult to design and implement and deploy tools that can successfully improve that quality.
Lastly,
consider the task of training a   novice software engineers or newcomers to a project. If our models are not stable, then it hard to teach what factors  most influence software quality.}
